Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Need quotes

What would happen if we used our approach to solve the maximum common induced problem? We could
simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
problem in the opposite direction from existing approaches, which work by attempting to construct
larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
\citet{DBLP:conf/cp/McCreeshNPS16}.  Recalling the disclaimer in \cref{section:setup}
regarding instances not fitting in the 64GBytes of RAM we have available, we see that our approach is
able to close over twice as many of these instances as the previous state of the art. (The same
conclusion holds even if every instance which is satisfiable with $k = 0$ is removed from the
dataset.)

>>>>

What would happen if we used our approach to solve the maximum common induced problem? We could
simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
problem in the opposite direction from existing approaches, which work by attempting to construct
larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: ``$k
\downarrow$'' is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
\citet{DBLP:conf/cp/McCreeshNPS16}.  Recalling the disclaimer in \cref{section:setup}
regarding instances not fitting in the 64GBytes of RAM we have available, we see that our approach is
able to close over twice as many of these instances as the previous state of the art. (The same
conclusion holds even if every instance which is satisfiable with $k = 0$ is removed from the
dataset.)
